The Astropy Project:

### 2017-09-29 main.tex
Update on Overleaf.
coordinates

The \texttt{astropy.coordinates} subpackage is designed to support representing
and transforming celestial coordinates and velocities.

>>>>

The \texttt{astropy.coordinates} subpackage is designed to support representing
and transforming celestial coordinates and, new in version 2.0, velocities.
A key concept behind the design of this subpackage is that coordinate
\textit{representations} and \textit{reference systems / frames} are independent
of one another.
For example, a set of coordinates in the International Celestial Reference
System (ICRS) reference frame could be represented as a spherical (distance,
right ascension, declination) or Cartesian coordinates.
They can therefore be re-represented or transformed to other reference frames
(e.g., the Galactic frame) in an independent way.
